---
title: "1_Plotting_and_Summarizing_the_Original_Models"
author: "Jennifer McHenry"
date: "08/30/2022"
output: html_document
---

# Script Purpose

This script was written with the intention of plotting and summarizing the final ecosystem service models for the paper. This is part of my dissertation work on marine ecosystem services from sea grasses in Florida. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(RColorBrewer)
library(mgcv)
library(tools)
library(viridis)
library(ggpubr)
# library(ggsn)
library(remotes)
library(raster)
# remotes::install_version("Rttf2pt1", version = "1.3.8")
library(extrafont)
library(ggcorrplot)
# extrafont::font_import() 
loadfonts("win")
library(ggplot2)
library(corrplot)
library(colorspace)
library(rgeos)


wd=getwd()

username=as.vector(strsplit(wd,"/"));names(username)<-c("username")

Saved_RData_Dir=paste("C:/Users/",username$username[3],"/Dropbox/GITHUB/Disseratation/",sep="")

```

#Functions
```{r}
pal_teal_blue_purple <- rainbow(12)

odds_to_prob=function(x){
        prob<-exp(x)/(1+exp(x))
        return(prob)
}


```

#loading masking and spatial domain data
```{r}
memory.limit(40000)
#loading data masks
Seagrass_Cover=raster(paste(Saved_RData_Dir,"Modeling_Biodiversity_Enhancement_Value/model_output/August_2020_seagrassmodel_predictions/Annual_Predictions/Seagrass_Cover_MeanAnnual_Current_Corrected_CorExp.tif",sep=""))
names(Seagrass_Cover)<-c("Seagrass_Cover")

#Total Predicted_Seagrass
Total_Predicted_Seagrass=Seagrass_Cover
Total_Predicted_Seagrass[Total_Predicted_Seagrass<5]<-NA
Total_Predicted_Seagrass[Total_Predicted_Seagrass>=5]<-0

# Study area
study_area<-raster("input_data/study_area.tif")

#masking the seagrass datasets
Total_Predicted_Seagrass=mask(Total_Predicted_Seagrass,mask = study_area)

#Confirmed Seagrass Areas
Confirmed=raster("input_data/seagrass_area_masks/confirmed_seagrass_beds.tif")
Confirmed=mask(Confirmed,mask = study_area)

Seagrass_Cover_Confirmed=mask(Seagrass_Cover,mask=Confirmed)


#loading regions raster
FCMap=raster("input_data/FCMaP_Workshop_Regions/FCMaP.tif")
FCMap=resample(x=FCMap,y = study_area,method="ngb")

```

#Loading ES outputs (Raw)
```{r}
#loading ES maps
BioDiv_EV_Raw=raster("input_data/ES-Model-Outputs/BioDiv_EV_Raw_Confirmed.tif")
NurHab_EV_Raw=raster("input_data/ES-Model-Outputs/NursHab_EV_Raw_Confirmed.tif")
Gray_Snapper_EV_Raw=raster("input_data/ES-Model-Outputs/Gray_Snapper_EV_Raw_Confirmed.tif")
Lane_Snapper_EV_Raw=raster("input_data/ES-Model-Outputs/Lane_Snapper_EV_Raw_Confirmed.tif")
White_Grunt_EV_Raw=raster("input_data/ES-Model-Outputs/White_Grunt_EV_Raw_Confirmed.tif")
Spotted_Seatrout_EV_Raw=raster("input_data/ES-Model-Outputs/Spotted_Seatrout_EV_Raw_Confirmed.tif")
Sheepshead_EV_Raw=raster("input_data/ES-Model-Outputs/Sheepshead_EV_Raw_Confirmed.tif")
Pink_Shrimp_EV_Raw=raster("input_data/ES-Model-Outputs/Pink_Shrimp_EV_Raw_Confirmed.tif")
BlueCar_EV_Raw=raster("input_data/ES-Model-Outputs/BC_Emissions_EV_Raw_Confirmed.tif")
RecTour_EV_Raw=raster("input_data/ES-Model-Outputs/Rec_EV_Raw_Confirmed.tif")
Expos_EV_Raw=raster("input_data/ES-Model-Outputs/Exposure_EV_Raw_Confirmed.tif")

ES_Raw=stack(FCMap,Seagrass_Cover,BioDiv_EV_Raw,NurHab_EV_Raw,Gray_Snapper_EV_Raw,Lane_Snapper_EV_Raw,White_Grunt_EV_Raw,Spotted_Seatrout_EV_Raw,Sheepshead_EV_Raw,Pink_Shrimp_EV_Raw,BlueCar_EV_Raw,RecTour_EV_Raw,Expos_EV_Raw)

ES_Raw=mask(ES_Raw,mask=Confirmed)
ES_Raw_df=as.data.frame(rasterToPoints(ES_Raw))
names(ES_Raw_df)<-c("x","y","Regions","Seagrass_Cover","BioDiv","NurHab","Gray_Snapper","Lane_Snapper","White_Grunt","Spotted_Seatrout","Sheepshead","Pink_Shrimp","BlueCar","RecTour","Expos")
ES_Raw_df<-ES_Raw_df[complete.cases(ES_Raw_df),]
summary(ES_Raw_df)

```

#Testing for signficance of overall enhancement (Raw)
```{r}
#Wilcoxon two sided rank sum test 
#biodiversity enhancement
wilcox.test(ES_Raw_df$BioDiv,alternative = "two.sided")
wilcox.test(ES_Raw_df$NurHab,alternative = "two.sided")
wilcox.test(ES_Raw_df$Gray_Snapper,alternative = "two.sided")
wilcox.test(ES_Raw_df$Pink_Shrimp,alternative = "two.sided")
wilcox.test(ES_Raw_df$Lane_Snapper,alternative = "two.sided")
wilcox.test(ES_Raw_df$Spotted_Seatrout,alternative = "two.sided")
wilcox.test(ES_Raw_df$Sheepshead,alternative = "two.sided")
wilcox.test(ES_Raw_df$White_Grunt,alternative = "two.sided")
wilcox.test(ES_Raw_df$BlueCar,alternative = "two.sided")
wilcox.test(ES_Raw_df$RecTour,alternative = "two.sided")
wilcox.test(ES_Raw_df$Expos,alternative = "two.sided")
```

#Spatial Correlations (Raw)
```{r}
round(cor(ES_Raw_df[c(5:15)]),1)

##Pearson Correlations 
ES_Raw_cors_df<-ES_Raw_df

names(ES_Raw_cors_df)<-c("Longitude","Latitude","Regions","Total Seagrass Cover","BE","NHE","NHE-GS","NHE-LS","NHE-WG","NHE-SS","NHE-S","NHE-PS","BCE","RE","CPE")

#main ecosystem services
ES_Raw_cors<-round(cor(ES_Raw_cors_df[c(5:6,13:15)]),1)


corrplot(ES_cors, type = 'lower', order = 'hclust', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = COL2('PRGn', 10),addCoef.col = 'black',diag=FALSE)

```

#Summarizing Regional Differences (Raw)
```{r}
#average for regions
ES_study_area_summary_df <- ES_Raw_df%>%
  select(Regions:Expos)%>%
  mutate(Regions=ifelse(Regions==1,"2_Big_Bend",ifelse(Regions==2,"4_South",ifelse(Regions==4,"1_Panhandle","3_South_Central"))))%>%
  pivot_longer(names_to = "ES",cols = BioDiv:Expos,values_to = "Raw_Value")%>%
  group_by(ES)%>%
  summarize(mean=mean(Raw_Value,na.rm=TRUE))%>%
  pivot_wider(names_from=ES,values_from = mean)

#CV for regions
ES_study_area_CV_df <- ES_Raw_df%>%
  select(Regions:Expos)%>%
  mutate(Regions=ifelse(Regions==1,"2_Big_Bend",ifelse(Regions==2,"4_South",ifelse(Regions==4,"1_Panhandle","3_South_Central"))))%>%
  pivot_longer(names_to = "ES",cols = BioDiv:Expos,values_to = "Raw_Value")%>%
  group_by(ES)%>%
  summarize(CV=cv(Raw_Value,na.rm=TRUE))%>%
  pivot_wider(names_from=ES,values_from = CV)

#average for regions
ES_regional_summary_df <- ES_Raw_df%>%
  select(Regions:Expos)%>%
  mutate(Regions=ifelse(Regions==1,"2_Big_Bend",ifelse(Regions==2,"4_South",ifelse(Regions==4,"1_Panhandle","3_South_Central"))))%>%
  pivot_longer(names_to = "ES",cols = BioDiv:Expos,values_to = "Raw_Value")%>%
  group_by(Regions,ES)%>%
  summarize(mean=mean(Raw_Value,na.rm=TRUE))%>%
  pivot_wider(id_cols=Regions,names_from=ES,values_from = mean)


p_boxplot<- ES_Raw_df%>%
  select(Regions,BioDiv,NurHab,BlueCar:Expos)%>%
  mutate(Regions=ifelse(Regions==1,"2_Big_Bend",ifelse(Regions==2,"4_South",ifelse(Regions==4,"1_Panhandle","3_South_Central"))))%>%
  pivot_longer(names_to = "ES",cols = BioDiv:Expos,values_to = "Raw_Value")%>%
  # group_by(Regions,ES)%>%
  ggplot(aes(x=Raw_Value,fill=Regions))+geom_histogram(position="stack")+facet_wrap(~ES,scales="free_y")


```

#Loading ES Outputs (Standarized)
```{r}
#loading ES maps
BioDiv_EV=raster("input_data/ES-Model-Outputs/BioDiv_EV_Zscores_Confirmed.tif")
NurHab_EV=raster("input_data/ES-Model-Outputs/NursHab_EV_Zscores_Confirmed.tif")
Gray_Snapper_EV=raster("input_data/ES-Model-Outputs/Gray_Snapper_EV_Zscores_Confirmed.tif")
Lane_Snapper_EV=raster("input_data/ES-Model-Outputs/Lane_Snapper_EV_Zscores_Confirmed.tif")
White_Grunt_EV=raster("input_data/ES-Model-Outputs/White_Grunt_EV_Sscores_Confirmed.tif")
Spotted_Seatrout_EV=raster("input_data/ES-Model-Outputs/Spotted_Seatrout_EV_Zscores_Confirmed.tif")
Sheepshead_EV=raster("input_data/ES-Model-Outputs/Sheepshead_EV_Zscores_Confirmed.tif")
Pink_Shrimp_EV=raster("input_data/ES-Model-Outputs/Pink_Shrimp_EV_Zscores_Confirmed.tif")
BlueCar_EV=raster("input_data/ES-Model-Outputs/BC_Storage_EV_Zscores_Confirmed.tif")
RecTour_EV=raster("input_data/ES-Model-Outputs/Rec_EV_Zscores_Confirmed.tif")
Expos_EV=raster("input_data/ES-Model-Outputs/Exposure_EV_Zscores_Confirmed.tif")
Pop_EV=raster("input_data/ES-Model-Outputs/Population_EV_Zscores_Confirmed.tif")

ES_Zscores=stack(FCMap,Seagrass_Cover_Confirmed,BioDiv_EV,NurHab_EV,Gray_Snapper_EV,Lane_Snapper_EV,White_Grunt_EV,Spotted_Seatrout_EV,Sheepshead_EV,Pink_Shrimp_EV,BlueCar_EV,RecTour_EV,Expos_EV,Pop_EV)

ES_Zscores=mask(ES_Zscores,mask=Confirmed)
ES_Zscores_df=as.data.frame(rasterToPoints(ES_Zscores))
names(ES_Zscores_df)<-c("x","y","Regions","Seagrass_Cover","BioDiv","NurHab","Gray_Snapper","Lane_Snapper","White_Grunt","Spotted_Seatrout","Sheepshead","Pink_Shrimp","BlueCar","RecTour","Expos","Pop")
ES_Zscores_df<-ES_Zscores_df[complete.cases(ES_Zscores_df),]
summary(ES_Zscores_df)
```

# Spatial overlap of hotspots
```{r}
ES_hotspots=raster("input_data/ES-Model-Outputs/ES_hotspots_Confirmed.tif")

# Seagrass beds with zero ES hotspots ############################################################
ES_hotspots0 <- ES_hotspots
ES_hotspots0[ES_hotspots0 != 0] <- NA

#calculate area
#get sizes of all cells
cell_size<-area(ES_hotspots0, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots0<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of seagrasses with 0 ES hotspots:",round(area_hotspots0, digits=1),"km2"))


# Seagrass beds with 1 ES hotspots ############################################################
ES_hotspots1 <- ES_hotspots
ES_hotspots1[ES_hotspots1 != 1] <- NA

#calculate area
#get sizes of all cells
cell_size<-area(ES_hotspots1, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots1<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of seagrasses with 1 ES hotspots:",round(area_hotspots1, digits=1),"km2"))

# Seagrass beds with 2 ES hotspots ############################################################
ES_hotspots2 <- ES_hotspots
ES_hotspots2[ES_hotspots2 != 2] <- NA

#calculate area
#get sizes of all cells
cell_size<-area(ES_hotspots2, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots2<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of seagrasses with 2 ES hotspots:",round(area_hotspots2, digits=1),"km2"))

# Seagrass beds with 3 ES hotspots ############################################################
ES_hotspots3 <- ES_hotspots
ES_hotspots3[ES_hotspots3 != 3] <- NA

#calculate area
#get sizes of all cells
cell_size<-area(ES_hotspots3, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots3<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of seagrasses with 3 ES hotspots:",round(area_hotspots3, digits=1),"km2"))

# Seagrass beds with 4 ES hotspots ############################################################
ES_hotspots4 <- ES_hotspots
ES_hotspots4[ES_hotspots4 != 4] <- NA

#calculate area
#get sizes of all cells
cell_size<-area(ES_hotspots4, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots4<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of seagrasses with 4 ES hotspots:",round(area_hotspots4, digits=1),"km2"))

# Seagrass beds with 5 ES hotspots ############################################################
ES_hotspots5 <- ES_hotspots
ES_hotspots5[ES_hotspots5 != 5] <- NA

#calculate area
#get sizes of all cells
cell_size<-area(ES_hotspots5, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots5<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of seagrasses with 5 ES hotspots:",round(area_hotspots5, digits=1),"km2"))


# All confirmed seagrass beds ############################################################

#calculate area
#get sizes of all cells
cell_size<-area(Confirmed, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
Confirmed_area<-length(cell_size)*median(cell_size)

#print area
print(paste("Area of all seagrasses:",round(Confirmed_area, digits=1),"km2"))


# Making a table

ES_hotspot_area_table=as.data.frame(rbind(area_hotspots0, area_hotspots1, area_hotspots2,area_hotspots3, area_hotspots4, area_hotspots5))
ES_hotspot_area_table$no_ES_hotspots<-0:5
names(ES_hotspot_area_table)<-c("area_km2","no_ES_hotspots")
rownames(ES_hotspot_area_table)<-NULL

ES_hotspot_area_table=ES_hotspot_area_table%>%
  select(no_ES_hotspots,area_km2)%>%
  dplyr::mutate(area_ha=area_km2*100,percent_total=(area_ha/(Confirmed_area*100)*100))


####################################################################################################################
#Calculating % overlap
BioDiv_Hotspot_1z=BioDiv_EV
BioDiv_Hotspot_1z[BioDiv_Hotspot_1z<1]<-NA
BioDiv_Hotspot_1z[BioDiv_Hotspot_1z>=1]<-1

NurHab_EV_1z=NurHab_EV
NurHab_EV_1z[NurHab_EV_1z<1]<-NA
NurHab_EV_1z[NurHab_EV_1z>=1]<-1

BlueCar_EV_1z=BlueCar_EV
BlueCar_EV_1z[BlueCar_EV_1z<1]<-NA
BlueCar_EV_1z[BlueCar_EV_1z>=1]<-1

RecTour_EV_1z=RecTour_EV
RecTour_EV_1z[RecTour_EV_1z<1]<-NA
RecTour_EV_1z[RecTour_EV_1z>=1]<-1

Expos_EV_1z=Expos_EV
Expos_EV_1z[Expos_EV_1z<1]<-NA
Expos_EV_1z[Expos_EV_1z>=1]<-1


#Intersection 
#biodiversity vs nursery
Overlap_Bio_Nurs=BioDiv_Hotspot_1z+NurHab_EV_1z

cell_size<-area(Overlap_Bio_Nurs, na.rm=TRUE, weights=FALSE)

#delete NAs from vector of all raster cells
##NAs lie outside of the rastered region, can thus be omitted
cell_size<-cell_size[!is.na(cell_size)]

#compute area [km2] of all cells in geo_raster
area_hotspots5<-length(cell_size)*median(cell_size)

```

# Spatial Correlations (Standardized ES) 
```{r}
# pal <- choose_palette()

##Pearson Correlations 
ES_cors_df<-ES_Zscores_df

names(ES_cors_df)<-c("Longitude","Latitude","Regions","Total Seagrass Cover","Biodiversity","Nursery Habitat","Gray Snapper","Lane Snapper","White Grunt","Spotted Seatrout","Sheepshead","Pink Shrimp","Blue Carbon","Recreation","Coastal Protection","Coastal Population")

#main ecosystem services
ES_cors<-round(cor(ES_cors_df[c(5:6,13:16)]),1)
ES_cors<-round(cor(ES_cors_df[c(5:6,13:15)]),1)

corrplot(ES_cors, type = 'lower', order = 'original', tl.col = 'black',
          cl.ratio = 0.2, tl.srt = 45,
         # col = diverge_hcl(8,h=c(180,290),l=c(40,95)),
         col=viridis(8),
         addCoef.col = 'black',diag=FALSE)
#saving the output
tiff("plots/Figure_3_RWB.tiff", units="in", width=5, height=5, res=300)

corrplot(ES_cors, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, 
                  # col=viridisviridis(8),
        col= colorRampPalette(c("red","white","blue"))(10),
         addCoef.col = 'black',diag=FALSE)

dev.off()



#expanded nursery habita tand other services
ES_cors_expanded<-round(cor(ES_cors_df[c(5,7:15)]),2)

#saving the output
tiff("plots/Figure_S4.tiff", units="in", width=7, height=7, res=300)
corrplot(ES_cors_expanded, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)
dev.off()


```

# Individual Variation (Standardized ES)
```{r}

ES_Zscores_long_df<-ES_Zscores_df%>%
  dplyr::select(Regions,BioDiv,NurHab,BlueCar:Expos)%>%
  pivot_longer(cols=BioDiv:Expos,names_to="ES",values_to="ZScores")%>%
  mutate(ES=factor(ES,levels=c("BioDiv","NurHab","BlueCar","RecTour","Expos"),labels=c("Biodiversity Enhancement","Nursery Habitat","Blue Carbon Storage","Recreational Use","Coastal Protection")))

p1=ES_Zscores_long_df%>%
  ggplot(aes(y=ZScores,x=ES,fill=ES),colour="black")+geom_violin(trim=FALSE) + geom_boxplot(width=0.1)+ xlab("Frequency of Value") + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none")+scale_fill_manual(values=pal_teal_blue_purple[c(7,8,9,11,12)]) +ylab("Ecosystem Service Value (Z-Score)")

p1

#saving the output
tiff("plots/Figure_2.tiff", units="in", width=8, height=12, res=300)
p1
dev.off()

```

## seagrass cover level
```{r}
p1_cover_levels<-ES_Zscores_df%>%
  mutate(cover_levels=ifelse(Seagrass_Cover>=75,"high",ifelse(Seagrass_Cover>=50 & Seagrass_Cover<75,"medium",ifelse(Seagrass_Cover>=25 & Seagrass_Cover<50,"low","sparse"))),cover_levels=factor(cover_levels,levels=c("high","medium","low","sparse")))%>%
  dplyr::select(Regions,cover_levels,BioDiv,NurHab,BlueCar:Expos)%>%
  pivot_longer(cols=BioDiv:Expos,names_to="ES",values_to="ZScores")%>%
  mutate(ES=factor(ES,levels=c("BioDiv","NurHab","BlueCar","RecTour","Expos"),labels=c("Biodiversity Enhancement","Nursery Habitat","Blue Carbon Storage","Recreational Use","Coastal Protection")))%>%
  ggplot(aes(y=ZScores,x=ES,fill=cover_levels))+geom_boxplot(position = "dodge") + xlab("Frequency of Value") + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none")+scale_fill_manual(values=pal_teal_blue_purple[c(7,8,9,11,12)]) +ylab("Ecosystem Service Value (Z-Score)")
  

```

#regional plot - zscores
```{r}
ES_Zscores_regional_summary<-ES_Zscores_long_df%>%
  group_by(Regions,ES)%>%
  summarize(mean=mean(ZScores))

p1_regions<- ES_Zscores_df%>%
  select(Regions,BioDiv,NurHab,BlueCar:Expos)%>%
  pivot_longer(names_to = "ES",cols = BioDiv:Expos,values_to = "Raw_Value")%>%
    mutate(Regions=factor(Regions,levels=c(2,6,1,4),labels=c("South","Central","Big Bend","Panhandle")))%>%
    mutate(ES=factor(ES,levels=c("BioDiv","NurHab","BlueCar","RecTour","Expos"),labels=c("BE","NHE","BCE","RE","CPE")))%>%
  # group_by(Regions,ES)%>%
  ggplot(aes(x=Raw_Value,y=(Regions),fill=(Regions)))+geom_boxplot()+ facet_wrap(~ES)+ geom_vline(xintercept = 0,color="grey50",size=1) + ylab("Ecosystem Services") + xlab("Standardized Enahancement Values (Z-Score)") + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none")+scale_fill_manual(values=pal_teal_blue_purple[c(7,8,10,11)]) 

#saving the output
tiff("plots/Figure_region_boxplots.tiff", units="in", width=8, height=6, res=300)
p1_regions
dev.off()

```

#regional plot - correlations
```{r}
#Pandhandle 
ES_cors_Panhandle_df<-ES_Zscores_df%>%
  mutate(Regions=factor(Regions,levels=c(2,6,1,4),labels=c("South","Central","Big Bend","Panhandle")))%>%
  filter(Regions=="Panhandle")

names(ES_cors_Panhandle_df)<-c("Longitude","Latitude","Regions","Total Seagrass Cover","Biodiversity","Nursery Habitat","Gray Snapper","Lane Snapper","White Grunt","Spotted Seatrout","Sheepshead","Pink Shrimp","Blue Carbon","Recreation","Coastal Protection","Coastal Population")

#main ecosystem services
ES_cors_Panhandle<-round(cor(ES_cors_Panhandle_df[c(5:6,13:15)]),1)


corrplot(ES_cors_Panhandle,  type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)


#saving the output
tiff("plots/Figure_4_panhandle.tiff", units="in", width=5, height=5, res=300)
corrplot(ES_cors_Panhandle, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)


# Big Bend
ES_cors_Big_Bend_df<-ES_Zscores_df%>%
  mutate(Regions=factor(Regions,levels=c(2,6,1,4),labels=c("South","Central","Big Bend","Panhandle")))%>%
  filter(Regions=="Big Bend")

names(ES_cors_Big_Bend_df)<-c("Longitude","Latitude","Regions","Total Seagrass Cover","Biodiversity","Nursery Habitat","Gray Snapper","Lane Snapper","White Grunt","Spotted Seatrout","Sheepshead","Pink Shrimp","Blue Carbon","Recreation","Coastal Protection","Coastal Population")

#main ecosystem services
ES_cors_Big_Bend<-round(cor(ES_cors_Big_Bend_df[c(5:6,13:15)]),1)


corrplot(ES_cors_Big_Bend, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)

#saving the output
tiff("plots/Figure_4_big_bend.tiff", units="in", width=5, height=5, res=300)
corrplot(ES_cors_Big_Bend, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)
dev.off()


# Central Florida
ES_cors_Central_df<-ES_Zscores_df%>%
  mutate(Regions=factor(Regions,levels=c(2,6,1,4),labels=c("South","Central","Big Bend","Panhandle")))%>%
  filter(Regions=="Central")

names(ES_cors_Central_df)<-c("Longitude","Latitude","Regions","Total Seagrass Cover","Biodiversity","Nursery Habitat","Gray Snapper","Lane Snapper","White Grunt","Spotted Seatrout","Sheepshead","Pink Shrimp","Blue Carbon","Recreation","Coastal Protection","Coastal Population")

#main ecosystem services
ES_cors_Central<-round(cor(ES_cors_Central_df[c(5:6,13:15)]),1)


corrplot(ES_cors_Central, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)

#saving the output
tiff("plots/Figure_4_central.tiff", units="in", width=5, height=5, res=300)
corrplot(ES_cors_Central, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)
dev.off()

#South Florida
ES_cors_South_df<-ES_Zscores_df%>%
  mutate(Regions=factor(Regions,levels=c(2,6,1,4),labels=c("South","Central","Big Bend","Panhandle")))%>%
  filter(Regions=="South")

names(ES_cors_South_df)<-c("Longitude","Latitude","Regions","Total Seagrass Cover","Biodiversity","Nursery Habitat","Gray Snapper","Lane Snapper","White Grunt","Spotted Seatrout","Sheepshead","Pink Shrimp","Blue Carbon","Recreation","Coastal Protection","Coastal Population")

#main ecosystem services
ES_cors_South<-round(cor(ES_cors_South_df[c(5:6,13:15)]),1)


corrplot(ES_cors_South, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)

#saving the output
tiff("plots/Figure_4_south.tiff", units="in", width=5, height=5, res=300)
corrplot(ES_cors_South, type = 'lower', order = 'original', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = diverge_hcl(8,h=c(190,290),l=c(40,95)),addCoef.col = 'black',diag=FALSE)
dev.off()

```

# Plotting relationships among ES
```{r}
library(paletteer); library(colorBlindness)

ES_Zscores_df_X=sample_n(ES_Zscores_df, 50000)

# Biodiversity and Nursery Habitat
p2=ES_Zscores_df_X%>%
  mutate(BioDiv=round(BioDiv,1),NurHab=round(NurHab,1))%>%
    ggplot(aes(y=BioDiv, x=NurHab, fill=stat(count)*93^2*0.0001))+ 
  labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) + 
  ggtitle("") + 
  theme_classic(base_size = 16, base_family = "Calibri")+
  theme(legend.position="right") +ylab("Biodiversity Enhancment") +
  xlab("Nursery Habitat")+
  scale_fill_distiller(palette = "BuPu",direction = 1)+ 
  geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+
  geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1) 

# Biodiversity and Carbon Storage
p3=ES_Zscores_df_X%>%
  mutate(BioDiv=round(BioDiv,1),BlueCar=round(BlueCar,1))%>%
    ggplot(aes(y=BioDiv, x=BlueCar, fill=stat(count)*93^2*0.0001))+ 
  labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) + 
                                    ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +ylab("Biodiversity Enhancment") + xlab("Blue Carbon Storage")+scale_fill_distiller(palette = "BuPu",direction = 1)+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Biodiversity and Recreation
p4=ES_Zscores_df_X%>%
  mutate(BioDiv=round(BioDiv,1),RecTour=round(RecTour,1))%>%
    ggplot(aes(y=BioDiv, x=RecTour, fill=stat(count)*93^2*0.0001))+  labs(fill="Hectares")+
  geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +ylab("Biodiversity Enhancment") + xlab("Recreational Use")+scale_fill_distiller(palette = "BuPu",direction = 1)+geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Biodiversity and Coastal Protection
p5=ES_Zscores_df_X%>%
  mutate(BioDiv=round(BioDiv,1),Expos=round(Expos,1))%>%
    ggplot(aes(y=BioDiv, x=Expos, fill=stat(count)*93^2*0.0001))+ labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000))+ ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +ylab("Biodiversity Enhancment") + xlab("Coastal Protection")+scale_fill_distiller(palette = "BuPu",direction = 1)+geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Nursery Habitat and Carbon Storage
p6=ES_Zscores_df_X%>%
    mutate(NurHab=round(NurHab,1),BlueCar=round(BlueCar,1))%>%
    ggplot(aes(y=NurHab, x=BlueCar, fill=stat(count)*93^2*0.0001))+ 
  labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) +  ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +xlab("Blue Carbon Storage") + ylab("Nursery Habitat")+scale_fill_distiller(palette = "BuPu",direction = 1)+geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Nursery Habitat and Recreation
p7=ES_Zscores_df_X%>%
    mutate(NurHab=round(NurHab,1),RecTour=round(RecTour,1))%>%
    ggplot(aes(y=NurHab, x=RecTour, fill=stat(count)*93^2*0.0001))+ 
  labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) +   ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +xlab("Recreational Use") + ylab("Nursery Habitat")+scale_fill_distiller(palette = "BuPu",direction = 1)+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Nursery Habitat and Coastal Protection
p8=ES_Zscores_df_X%>%
    mutate(NurHab=round(NurHab,1),Expos=round(Expos,1))%>%
    ggplot(aes(y=NurHab, x=Expos, fill=stat(count)*93^2*0.0001))+ labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +xlab("Coastal Protection") + ylab("Nursery Habitat")+scale_fill_distiller(palette = "BuPu",direction = 1)+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Carbon Storage and Recreation 
p9=ES_Zscores_df_X%>%
    mutate(RecTour=round(RecTour,1),BlueCar=round(BlueCar,1))%>%
    ggplot(aes(y=BlueCar, x=RecTour,fill=stat(count)*93^2*0.0001))+  labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) +  ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +ylab("Blue Carbon Storage") + xlab("Recreational Use")+scale_fill_distiller(palette = "BuPu",direction = 1)+geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Carbon Storage and Coastal Protection 
p10=ES_Zscores_df_X%>%
    mutate(RecTour=round(RecTour,1),Expos=round(Expos,1))%>%
    ggplot(aes(y=BlueCar, x=Expos,fill=stat(count)*93^2*0.0001))+ labs(fill="Hectares")+ geom_hex(bins=5,color="black",
                                  limts=c(0,6000)) +  ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="right") +ylab("Blue Carbon Storage") + xlab("Coastal Protection")+ scale_fill_distiller(palette = "BuPu",direction = 1)+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)
# Recreation and Coastal Protection 

#blank
blank=ES_Zscores_df_X%>%
    ggplot(aes(y=NurHab, x=Expos))+xlab("")+ylab("")+theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none",
          panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),plot.background=element_blank())
#saving the output
tiff("plots/Figure_3a.tiff", units="in", width=16, height=3, res=300)
ggarrange(p2,p3,p4,p5,nrow = 1, ncol=4, widths = c(2,2,2,2),heights = c(1,1,1,1))
dev.off()

tiff("plots/Figure_3b.tiff", units="in", width=16, height=3, res=300)
ggarrange(blank,p6,p7,p8,nrow = 1, ncol=4,widths = c(2,2,2,2),heights = c(1,1,1,1))

tiff("plots/Figure_3c.tiff", units="in", width=16, height=3, res=300)
ggarrange(blank,blank,p9,p10,nrow = 1, ncol=4, widths = c(2,2,2,2),heights = c(1,1,1,1))
dev.off()
```

# Accessibility figure 
```{r}
# Biodiversity and Population
p11=ES_Zscores_df_X%>%
  mutate(BioDiv=round(BioDiv,1),Pop=round(Pop,1))%>%
    ggplot(aes(y=BioDiv, x=Pop))+  geom_hex(bins=5,color="white")  + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none") +ylab("Biodiversity Enhancment (z-scores)") + xlab("Coastal Population (z-scores)")+scale_fill_viridis_c()+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Carbon Storage and Population
p12=ES_Zscores_df_X%>%
  mutate(NurHab=round(NurHab,1),Pop=round(Pop,1))%>%
    ggplot(aes(y=NurHab, x=Pop))+  geom_hex(bins=5,color="white")  + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none") +ylab("Nursery Habitat (z-scores)")+xlab("Coastal Population (z-scores)")+scale_fill_viridis_c()+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Carbon Storage and Population
p13=ES_Zscores_df_X%>%
  mutate(BlueCar=round(BlueCar,1),Pop=round(Pop,1))%>%
    ggplot(aes(y=BlueCar, x=Pop))+  geom_hex(bins=5,color="white")  + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none") +ylab("Blue Carbon Storage (z-scores)")+xlab("Coastal Population (z-scores)")+scale_fill_viridis_c()+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

#  Recreation and Population 
p14=ES_Zscores_df_X%>%
  mutate(RecTour=round(RecTour,1),Pop=round(Pop,1))%>%
    ggplot(aes(y=RecTour, x=Pop))+  geom_hex(bins=5,color="white")  + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none") +ylab("Recreational Use (z-scores)")+xlab("Coastal Population (z-scores)")+scale_fill_viridis_c()+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

# Biodiversity and Coastal Protection
p15=ES_Zscores_df_X%>%
  mutate(Expos=round(Expos,1),Pop=round(Pop,1))%>%
    ggplot(aes(y=Expos, x=Pop))+  geom_hex(bins=5,color="white")  + ggtitle("") + theme_classic(base_size = 16, base_family = "Calibri")+theme(legend.position="none") +ylab("Coastal Protection (z-scores)")+xlab("Coastal Population (z-scores)")+scale_fill_viridis_c()+ geom_hline(yintercept = 0, colour="#FF6600", linetype="dashed",size=1)+geom_vline(xintercept = 0, colour="#FF6600", linetype="dashed",size=1)

ggarrange(p11,p12,p13,p14,p15,nrow = 1, ncol=5, widths = c(1,1,1,1,1))

```


# Appendicies for individual model output
# Nursery Habitat Models Figure S2
```{r warning=FALSE}
data=read.csv(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/data/FIM_Final_NurserySpecies_1997_2017_wideform_meancovaraites_QAQC.csv",sep=""))

data=data%>%
  filter(Gear_Type=="SmallSeine" | Gear_Type=="OtterTrawl")%>%
  mutate(TH_PA=as.factor(TH_PA),SY_PA=as.factor(SY_PA),HA_PA=as.factor(HA_PA),Seagrass_PA=as.factor(Seagrass_PA),ST_Mangroves=as.factor(ST_Mangroves),ST_Oysters=as.factor(ST_Oysters),Mud=as.factor(Mud),Sand=as.factor(Sand),Rocks=as.factor(Rocks),Gear_Type=as.factor(Gear_Type))

purples_colors <- brewer.pal(9, "PuRd") %>%
  colorRampPalette()


#Pink Shrimp
pink_shrimp=readRDS(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/model_versions/nursery_habitat_final_models/Pink_Shrimp_binomial_gam.rds",sep=""))

pdf(file="plots/Partial_Response_Curves_Pink_Shrimp.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.1));
plot.gam(pink_shrimp,shade=TRUE,shade.col="pink",scheme=2,trans=odds_to_prob,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()


# Spotted Seatrout
spotted_seatrout=readRDS(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/model_versions/nursery_habitat_final_models/Spotted_Seatrout_binomial_gam.rds",sep=""))

pdf(file="plots/Partial_Response_Curves_Spooted_Seatrout.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.25));
plot.gam(spotted_seatrout,shade=TRUE,shade.col="pink",scheme=2,trans=odds_to_prob,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()


#Gray Snapper
gray_snapper=readRDS(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/model_versions/nursery_habitat_final_models/Gray_Snapper_binomial_gam.rds",sep=""))

pdf(file="plots/Partial_Response_Curves_Gray_Snapper.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.25));
plot.gam(gray_snapper,shade=TRUE,shade.col="pink",scheme=2,trans=odds_to_prob,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()

# Lane Snapper
lane_snapper=readRDS(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/model_versions/nursery_habitat_final_models/Lane_Snapper_binomial_gam.rds",sep=""))

pdf(file="plots/Partial_Response_Curves_Lane_Snapper.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.25));
plot.gam(lane_snapper,shade=TRUE,shade.col="pink",scheme=2,trans=odds_to_prob,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()

#White Grunt
white_grunt=readRDS(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/model_versions/nursery_habitat_final_models/WhiteGrunt_binomial_gam.rds",sep=""))

pdf(file="plots/Partial_Response_Curves_White_Grunt.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.25));
plot.gam(white_grunt,shade=TRUE,shade.col="pink",scheme=2,trans=odds_to_prob,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()

sheepshead=readRDS(paste(Saved_RData_Dir,"Modeling-NurseryHabitat-in-FLSeagrassBeds/model_versions/nursery_habitat_final_models/Sheepshead_binomial_gam.rds",sep=""))

pdf(file="plots/Partial_Response_Curves_Sheepshead.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.25));
plot.gam(sheepshead,shade=TRUE,shade.col="pink",scheme=2,trans=odds_to_prob,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()

```
# Blue Carbon Figure S3
```{r warning=FALSE}
#loading the modelg datasets
load(file=paste(Saved_RData_Dir,"Saved_RData/Blue_Carbon_Modeling_FALL2021_Shallow_FINAL.RData",sep=""))

rm(list= ls()[!(ls() %in% c("Saved_RData_Dir",
                            "Shallow_BlueCarbon_QAQC_Site_Level_By_DepthBin_ALLCORES",
                            "Total_Predicted_Seagrass", "Confirmed", "Unconfirmed",
                            "pal_teal_blue_purple","fl_shoreline","Atlantic_Mask"))])

organic_carbon_stock_ALLCORES=readRDS(paste(Saved_RData_Dir,"Modeling-Blue-Carbon-Storage-in-FLSeagrassBeds/model_versions/carbon_final_models/Organic_Carbon_Stock_SL_shallow_GAM_ALLCORES.rds",sep=""))

p1= pdp::partial(object=organic_carbon_stock_ALLCORES, pred.var = c("total_seagrass_cover"),plot.engine = "ggplot2",plot=TRUE,rug=TRUE, smooth=TRUE) +  xlab("Total Seagrass Cover (%)") +theme_classic(base_size = 16, base_family = "Calibri") +ylim(7,16) +ggtitle("a.")

p2=pdp::partial(object=organic_carbon_stock_ALLCORES, pred.var = c("percent_silt"),plot.engine = "ggplot2",plot=TRUE,rug=TRUE, smooth=TRUE) +xlab("Silt Content (%)")+theme_classic(base_size = 16, base_family = "Calibri")+ylim(7,16)

p3=pdp::partial(object=organic_carbon_stock_ALLCORES, pred.var = c("Dist_To_OysterReefs_km"), plot=TRUE, smooth=TRUE,rug=TRUE,plot.engine = "ggplot2")+ xlab("Distance to Oyster Reefs (km)") + theme_classic(base_size = 16, base_family = "Calibri")+ylim(7,16) 


#Figure 2
ggarrange(p1,p2,p3,nrow=1,ncol=3)

#saving the output
tiff("plots/Figure_S3.tiff", units="in", width=11, height=3, res=300)
ggarrange(p1,p2,p3,nrow=1,ncol=3)
dev.off()

```


```{r warning=FALSE}
purples_colors <- brewer.pal(9, "PuRd") %>%
  colorRampPalette()

final_recreation_model_gam=readRDS("model_versions/PUD_recreation_model_final.rds")
PUD_predictors_long=read.csv(file="model_versions/Flicker_PUD_raw_Predictors_long.csv")

pdf(file="plots/Partial_Response_Curves_Coastal_Visitation.pdf",onefile=T,width=6,height=6,pointsize=9)
par(mfrow=c(3,3),mai = c(0.5, 0.25, 0.25, 0.25));
plot.gam(final_recreation_model_gam,shade=TRUE,shift=coef(final_recreation_model_gam)[1],trans=exp,shade.col="pink",scheme=2,all.terms=TRUE,hcolors=purples_colors(20),too.far = 0.1)
dev.off()

```